Against the Planetary Interpretation of PTFO$\,$8-8695b

### 2020-03-28 paper/ms.tex
update paper
paper updates

%\begin{figure*}[t]
%	\begin{center}
%		\leavevmode
%		\includegraphics[width=0.95\textwidth]{f2.png}
%	\end{center}
%	\vspace{-0.7cm}
%	\caption{ {\bf foo.}
%    bar
%		\label{fig:lc_map}
%	}
%\end{figure*}

\begin{figure*}[t]
  \gridline{
    \fig{f3a.png}{0.8\textwidth}{}
    \fig{f3b.png}{0.2\textwidth}{}
  }
	\vspace{-0.7cm}
	\caption{ {\bf foo.}
    bar
		\label{fig:splitsignal}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f4.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf foo.}
    bar
		\label{fig:phasefold}
	}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene used for blend analysis.}
		{\it Top:} Mean TESS image of PTFO 8-8695 over Sector~6, with a log-stretch.
		The position of PTFO 8-8695 is shown with a yellow star.
		Neighbors with $T<17$ are shown with red crosses.
		The apertures used to measure the background and target star flux
		are shown with \texttt{X} and \texttt{/} hatches, respectively.
		{\it Bottom:} DDS2 $R$-band image of the same field, with a linear stretch. The circles show
		apertures of radii 1, 1.5, and 2.25 pixels used in part of our blend
		analysis.
		The pixel level TESS data show that ``Star A''  does not contribute variability at either of the two observed periods (see Section~\ref{subsec:blend}).
		\label{fig:scene}
	}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{o_minus_c.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf foo.}
		bar
		\label{fig:o_minus_c}
	}
\end{figure*}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{f1.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf TESS light-curve of PTFO 8-8695 (Sector 6, Orbit 1).}
	{\it Top}: ``Raw'' \texttt{PDCSAP} mean-subtracted relative flux versus time. The beat period of 4.48 days is visible by eye.
	The model plotted underneath the data includes 2 harmonics at the long
	period $P_{\rm \ell}$, plus 2 harmonics and a transit at the short period $P_{\rm s}$.
	{\it Upper middle}: Long-period signal, equal to the raw signal minus the short-period signal.
	{\it Lower middle}: Short-period signal, equal to the raw signal minus the long-period signal.
	{\it Bottom}: residual.
	The data are binned from 2 to 10 minute cadence as a convenience for plotting and fitting.
		\label{fig:splitsignal}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.95\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Phase-folded long and short-period signals.}
	{\it Top}: Long-period signal, as in Figure~\ref{fig:splitsignal}.
	{\it Bottom}: Short-period signal. The reference phase is set to the most ``planetary'' dip.
	Gray points are the 10 minute cadence \texttt{PDCSAP} flux.
	Black points are binned to 100 points per period.
	\label{fig:phasefold}
	}
\end{figure*}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene used for blend analysis.}
		{\it Top:} Mean TESS image of PTFO 8-8695 over Sector~6, with a log-stretch.
		The position of PTFO 8-8695 is shown with a yellow star.
		Neighbors with $T<17$ are shown with red crosses.
		The apertures used to measure the background and target star flux
		are shown with \texttt{X} and \texttt{/} hatches, respectively.
		{\it Bottom:} DDS2 $R$-band image of the same field, with a linear stretch. The circles show
		apertures of radii 1, 1.5, and 2.25 pixels used in part of our blend
		analysis.
		The pixel level TESS data show that ``Star A''  does not contribute variability at either of the two observed periods (see Section~\ref{subsec:blend}).
		\label{fig:scene}
	}
\end{figure}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf foo.}
		bar
		\label{fig:o_minus_c}
	}
\end{figure*}
